---
title: "FATCA"
author: "Charles"
date: "Tuesday, September 23, 2014"
output: html_document
---

## Create the read data structure

Context: 
- Website with data file updated on a monthly basis
- data file stucture remains the sale

Objective:
- download internet file and process them automatically

Function to consider
- f1 = globalread function
- f2 = file string function
- f3 = read csv

Code chunks:

```{r}
setwd("C:/Users/cberthillon/997.FATCA/project1")

#read function
f1 <- function(id, directory, summarize = FALSE) {
        f2 <- paste(getwd(),"/","001.data","/",sprintf("%06d", as.numeric(id)), ".csv", sep = "") #file sting function
        f3 <- read.csv(f2)
        if (summarize) {
                print(summary(f3))
        }
        return(f3)
}
data <- f1(201407, TRUE)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
